---
title: "Math_8452_hw1"
author: "Haichuan Du"
date: "6/3/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Size 5
```{r}
#First under the null hypothesis.
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=5, rate = 1)
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated alpha is:", nrej1/nruns))

#Now under an alternative.
shift=0.5
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=5, rate = 1) + shift
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated power is:", nrej1/nruns))
```

Size 10
```{r}
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=10, rate = 1)
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated alpha is:", nrej1/nruns))

#Now under an alternative.
shift=0.5
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=10, rate = 1) + shift
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated power is:", nrej1/nruns))
```

Size 20
```{r}
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=20, rate = 1)
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated alpha is:", nrej1/nruns))

#Now under an alternative.
shift=0.5
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=20, rate = 1) + shift
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated power is:", nrej1/nruns))
```

size 35
```{r}
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=35, rate = 1)
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated alpha is:", nrej1/nruns))

#Now under an alternative.
shift=0.5
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=35, rate = 1) + shift
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated power is:", nrej1/nruns))
```

Size 50
```{r}
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=50, rate = 1)
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated alpha is:", nrej1/nruns))

#Now under an alternative.
shift=0.5
set.seed(0) 
nruns=1000
nrej1=0
nrej2=0
for (run in 1:nruns){
  x=rexp(n=50, rate = 1) + shift
  if (t.test(x, mu=1)$p.value<0.05){nrej1=nrej1+1}}
print(paste("Estimated power is:", nrej1/nruns))
```
Comment:
The t-test is invalid for small samples from non-normal distributions, but it is valid for large samples from non-normal distributions. Non-normal population distributions, especially those that are thick-tailed 
or heavily skewed, considerably reduce the power of the test. Therefore, the test is robust when the sample size is large enough
