---
title: "HW#6"
author: "Haichuan Du"
date: "7/8/2020"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("~/Desktop/statistics/Nonparametric/project")
churn_data <- read.csv("churn.csv")
head(churn_data)
attach(churn_data)
```

```{r}
set.seed(0)
samp <- c(7, 10, 10, 10, 11, 12, 12, 13, 13, 14, 14, 15, 22, 31, 37)
n=length(samp)
B=1000 #Number of bootstrap samples to draw.
sdvec=double(B) #Saving the bootstrap standard deviations.
meavec=double(B) #Saving the bootstrap sample means.
coevar=double(B)
sd=sd(samp) #Observed standard deviation.
mea=mean(samp) #Observed sample mean.
cov=sd(samp)/mean(samp)
for (brun in 1:B){
  bsamp=sample(samp,n,replace=T) #Sample with replacement from the sample., 从sample里面取10次
  meavec[brun]=mean(bsamp)
  sdvec[brun]=sd(bsamp)
  coevar[brun]=sd(bsamp)/mean(bsamp)}
hist(meavec) #Plotting the bootstrap means.
abline(v=mea)

hist(sdvec) #Plotting the bootstrap standard deviations.
abline(v=sd)

#Now studying the mean.

ehat=mean(meavec) #Mean of the bootstrap values. -------point estimate
msehat=mean((meavec-mea)^2) #Estimated MSE.
se=sqrt(msehat) #Bootstrap SE---------> standard error.
bhat=ehat-mea #Estimated ----------> bootstrap bias.
CI=quantile(meavec,c(0.025,0.975))
ehat
msehat
se
bhat
CI


#Now studying the standard deviation.

ehat=mean(sdvec) #standard deviation. of the bootstrap values.----> point estimate
msehat=mean((sdvec-sd)^2) #Estimated MSE.
se=sqrt(msehat) #Bootstrap SE.
bhat=ehat-sd #Estimated bias.
CI=quantile(sdvec,c(0.025,0.975))
ehat
msehat
se
bhat
CI

#Now studying the  population coefficient of variation.

ehat=mean(coevar) #coefficient of variation of the bootstrap values.----> point estimate
msehat=mean((coevar-cov)^2) #Estimated MSE.
se=sqrt(msehat) #Bootstrap SE.
bhat=ehat-cov #Estimated bias.
CI=quantile(coevar,c(0.025,0.975))
ehat
msehat
se
bhat
CI
```
(a) For the population mean
point estimates = 15.39653
bootstrap standard errors =  2.0349
bootstrap bias estimates = -0.003466667
95% bootstrap percentile confidence intervals = (11.73333, 19.80167 )

(b) For the population standard deviation
point estimates = 7.659678
bootstrap standard errors =  2.312619
bootstrap bias estimates = -0.6624092
95% bootstrap percentile confidence intervals = (2.260737, 11.342461)

(c) For the population coefficient of variation
point estimates = 0.4897533
bootstrap standard errors =  0.1195191
bootstrap bias estimates = -0.050642
95% bootstrap percentile confidence intervals = (0.2021840, 0.6418488)

The population standard deviation is seriously biased(bootstrap bias estimates = -0.6624092)


#3
```{r}
sample_size <- churn_data$MonthlyCharges
length(sample_size)

plot(density(sample_size))

par(mfrow=c(2,2))
fit1=density(sample_size,kernel='gaussian') #Using default bandwidth.
fit2=density(sample_size,kernel='epanechnikov')
fit3=density(sample_size,kernel='rectangular')
fit4=density(sample_size,kernel='biweight')
plot(fit1,main='Gaussian')
plot(fit2,main='Epanechnikov')
plot(fit3,main='Rectangular')
plot(fit4,main='Biweight')

#Different bandwidths for gaussian kernal
par(mfrow=c(4,4))
plot(density(sample_size,kernel='gaussian',bw=0.1),main='')
plot(density(sample_size,kernel='gaussian',bw=1),main='')
plot(density(sample_size,kernel='gaussian',bw=3),main='')
plot(density(sample_size,kernel='gaussian',bw=5),main='')
plot(density(sample_size,kernel='gaussian',bw=10),main='')
plot(density(sample_size,kernel='gaussian',bw=20),main='')
plot(density(sample_size,kernel='gaussian',bw=25),main='')
plot(density(sample_size,kernel='gaussian',bw=30),main='')
plot(density(sample_size,kernel='gaussian',bw=40),main='')
plot(density(sample_size,kernel='gaussian',bw=50),main='')

#Different bandwidths for epanechnikov kernal
par(mfrow=c(4,4))
plot(density(sample_size,kernel='epanechnikov',bw=0.1),main='')
plot(density(sample_size,kernel='epanechnikov',bw=1),main='')
plot(density(sample_size,kernel='epanechnikov',bw=3),main='')
plot(density(sample_size,kernel='epanechnikov',bw=5),main='')
plot(density(sample_size,kernel='epanechnikov',bw=10),main='')
plot(density(sample_size,kernel='epanechnikov',bw=20),main='')
plot(density(sample_size,kernel='epanechnikov',bw=25),main='')
plot(density(sample_size,kernel='epanechnikov',bw=30),main='')
plot(density(sample_size,kernel='epanechnikov',bw=40),main='')
plot(density(sample_size,kernel='epanechnikov',bw=50),main='')

#Different bandwidths for rectangular kernal
par(mfrow=c(4,4))
plot(density(sample_size,kernel='rectangular',bw=0.1),main='')
plot(density(sample_size,kernel='rectangular',bw=1),main='')
plot(density(sample_size,kernel='rectangular',bw=3),main='')
plot(density(sample_size,kernel='rectangular',bw=5),main='')
plot(density(sample_size,kernel='rectangular',bw=10),main='')
plot(density(sample_size,kernel='rectangular',bw=20),main='')
plot(density(sample_size,kernel='rectangular',bw=25),main='')
plot(density(sample_size,kernel='rectangular',bw=30),main='')
plot(density(sample_size,kernel='rectangular',bw=40),main='')
plot(density(sample_size,kernel='rectangular',bw=50),main='')

#Different bandwidths for biweight kernal
par(mfrow=c(4,4))
plot(density(sample_size,kernel='biweight',bw=0.1),main='')
plot(density(sample_size,kernel='biweight',bw=1),main='')
plot(density(sample_size,kernel='biweight',bw=3),main='')
plot(density(sample_size,kernel='biweight',bw=5),main='')
plot(density(sample_size,kernel='biweight',bw=10),main='')
plot(density(sample_size,kernel='biweight',bw=20),main='')
plot(density(sample_size,kernel='biweight',bw=25),main='')
plot(density(sample_size,kernel='biweight',bw=30),main='')
plot(density(sample_size,kernel='biweight',bw=40),main='')
plot(density(sample_size,kernel='biweight',bw=50),main='')
```
(i) The sample size: Sample size for MonthlyCharges is 7043
(ii) The kernel that I used: Gaussian, Epanechnikov, Rectangular, Biweight
(iii) The bandwidth: The bandwidth I used incluing 0.1, 1, 3, 5, 10, 20, 25, 30, 40, 50
 
Comment on what the plot of the estimated density suggests about the shape of the distribution. Please indicate which bandwidths you tried (Do try some!) in addition to the default choice.

In general, with the constant increase of the bandwidth of the four kernels, the shape of the density gradually presents unimodal shape, approaching their original kernel function.

For gaussian kernel: When the bandwidth is less than 3, the density shape appears jagged; when the bandwidth is greater than 3 and less than 10, the density shape changes from 3 humps to 2; when the bandwidth is greater than 20, the density shape initially appears unimodal and tends to the original kernel function

For epanechnikov kernel: similar to to gaussian kernel, when the bandwidth <= 3, the density shape appears jagged; when the bandwidth is greater than 3 and less than 10, the density shape changes from 3 humps to 2 but has a smoother curve; when the bandwidth is greater than 20, the density shape initially appears unimodal and tends to the original kernel function。

For rectangular kernel: When the bandwidth is less than 10, the density shape is jagged, when the bandwidth is greater than 3 and less than 20, the hump gradually changes from 3 to 1 and the curve tends to be flat. When the bandwidth is greater than 25, the top shape of the hump tends to be close to the original kernel functio like straight line.

For biweight kernel: very similar to the gaussian kernel, gaussian kernel is little bit smoother than biweight.


      













